FinalManuscript_DISCS_UG

### 2018-06-26 parts/02_relatedliterature.tex
Added intro for chapter 2

@@

There are two kinds of cryptosystems, namely: \textit{symmetric} and \textit{asymmetric}. In symmetric-key cryptosystems, the same key is used for both encryption and decryption. As a consequence, the encryption and decryption functions are inverses of each other. Prominent examples of symmetric-key cryptosystems are the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).

>>>>

We first present an introduction to the concepts in cryptography, starting from the definition of a cryptosystem up to homomorphic encryption schemes, along with some examples from the literature. Then, we present some concepts in image processing, a suitable application of cryptography, specifically the common image operations used. Finally, we present related work that attempts to apply image processing operations with homomorphic cryptosystems, as well as their advantages and limitations.

@@

There are two kinds of cryptosystems, namely: \textit{symmetric} and \textit{asymmetric}. In symmetric-key cryptosystems, the same key is used for both encryption and decryption. As a consequence, the encryption and decryption functions are inverses of each other. Prominent examples of symmetric-key cryptosystems include the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).
